Parallel Global Optimization for Non-Convex Mixed-Integer Problems

### 2019-08-05 2019/RSD_Integer/RSD2019.tex

\title{Parallel Global Optimization for Non-Convex Mixed-Integer Problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}}
\author{Konstantin Barkalov \and Ilya Lebedev %\Letter 
\\
\email{ \{konstantin.barkalov,ilya.lebedev\}@itmm.unn.ru}}

@@

\keywords global optimization, non-convex constraints, mixed-integer problems.

@@

>>>>

\title{Parallel Global Optimization for Non-Convex Mixed-Integer Problems
%\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
\author{Konstantin Barkalov \and Ilya Lebedev %\Letter 
\\
\email{ \{konstantin.barkalov,ilya.lebedev\}@itmm.unn.ru}}

@@

\keywords { Global optimization, Non-convex constraints, Mixed-integer problems}

@@

\medskip

\textbf{Acknowledgments}. This study was supported by the Russian Science Foundation, project No.\,16-11-10150.
